\paragraph{Evaluation Metrics.}
We evaluate the learned hybrid automata from two perspectives: transition
timing and continuous-state reconstruction accuracy. Let $K$ denote the number
of evaluation traces. For the $k$-th trace, let
$\hat{m}^{(k)} = (\hat{m}^{(k)}_0,\ldots,\hat{m}^{(k)}_{T_k-1})$ and
$m^{(k)} = (m^{(k)}_0,\ldots,m^{(k)}_{T_k-1})$ be the inferred and ground-truth
mode sequences, respectively. The corresponding inferred and ground-truth state
trajectories are denoted by $\hat{x}^{(k)}_{i,t}$ and $x^{(k)}_{i,t}$, where
$i$ indexes the state variable and $t$ indexes the time step.

To assess the quality of mode switching, we first extract the change-point set
from a mode sequence $m$ as
\[
\mathrm{cp}(m)
=
\{0\}
\cup
\{t \mid 1 \le t \le T_k - 1,\; m_t \neq m_{t-1}\}
\cup
\{T_k\}.
\]
For two change-point sets $A$ and $B$, define the directed deviation
\[
d(A,B)=\max_{a\in A}\min_{b\in B}|a-b|.
\]
Then the transition-time error is defined as
\[
\mathrm{tc}
=
\max_{1\le k\le K}
\left(
\max
\left\{
d(\mathrm{cp}(\hat{m}^{(k)}),\mathrm{cp}(m^{(k)})),
d(\mathrm{cp}(m^{(k)}),\mathrm{cp}(\hat{m}^{(k)}))
\right\}
\cdot \Delta t
\right),
\]
where $\Delta t$ is the sampling interval. This metric measures the worst-case
symmetric mismatch between inferred and ground-truth switching times.

For the continuous dynamics, we use normalized absolute errors. For each
variable $i$ in trace $k$, let
\[
\varepsilon^{(k)}_{i,t}
=
\frac{\left|\hat{x}^{(k)}_{i,t}-x^{(k)}_{i,t}\right|}
{\max_{0\le \tau \le T_k-1}\left|x^{(k)}_{i,\tau}\right|}.
\]
Based on this normalized pointwise error, we report
\[
\mathrm{max\_diff}
=
\max_{1\le k\le K}\max_{i,t}\varepsilon^{(k)}_{i,t},
\]
which captures the worst-case normalized deviation, and
\[
\mathrm{mean\_diff}
=
\frac{1}{K}
\sum_{k=1}^{K}
\left(
\frac{1}{n_kT_k}
\sum_{i=1}^{n_k}\sum_{t=0}^{T_k-1}\varepsilon^{(k)}_{i,t}
\right),
\]
where $n_k$ is the number of state variables in the $k$-th trace. Hence,
$\mathrm{mean\_diff}$ is the average normalized absolute deviation across all
variables and time steps, averaged again over traces, while
$\mathrm{max\_diff}$ captures the largest normalized pointwise discrepancy.
